2H qSIP Calculations

### 2021-11-03 qSIP_calculations.Rmd
added save workspace image
added package info

```{r, message=FALSE, warning=FALSE}
# Libraries
library(tidyverse) # general data wrangling and plotting
library(forcats) # handling factors
library(isoreader) # reading the raw data files
library(isoprocessor) # processing the data
library(isotopia) # isotope utilities
library(readxl) # reading excel docs
library(ggsci) # some nice color palettes
library(ggborderline) # nice looking ggplot lines
library(ggrepel) # nice looking ggplot labels
library(latex2exp) # latex parsing
library(ggdist) # ggplot distribution geoms
library(ggsignif) # ggplot significance markers
library(ggridges) # ggplot ridgeline geoms

@@

@@

# Plots

## Peak Tracer Incorporation
```{r}
peaks_mapped_with_zeros_analytes %>% ggplot(
  aes(x = inc_time_d, y = at2H, color = compound, group = compound)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "loess") +
  #geom_borderline() +
  scale_color_viridis_d() +
  theme_minimal()
```

@@

```{r}
gen_calc_data_summarized %>% 
  mutate(compound = fct_reorder(compound, rt)) %>% 
  ggplot(aes(x = inc_time_d,
             y = at2H,
             color = compound)) +
  geom_borderline() +
  geom_point() +
  facet_wrap(vars(terrain)) +
  scale_x_continuous(breaks = c(0, 3, 7)) +
  scale_color_viridis_d() +
  theme_bw() +
  labs(x = "Incubation Time (Days)",
       y = "Mean %D")
```

>>>>

```{r, message=FALSE, warning=FALSE}
# Libraries
library(tidyverse)    # CRAN v1.3.1
library(forcats)      # CRAN v0.5.1 
library(isoreader)    # [::NA/NA] v1.3.0 # CRAN v1.3.0
library(isoprocessor) # [github::isoverse/isoprocessor] v0.6.7
library(isotopia)     # [github::isoverse/isotopia] v0.5.8 
library(readxl)       # CRAN v1.3.1 
library(ggsci)        # CRAN v2.9 
library(ggborderline) # [github::wurli/ggborderline] v0.1.0
library(ggrepel)      # CRAN v0.9.1 
library(latex2exp)    # CRAN v0.5.0
library(ggdist)       # CRAN v3.0.0 
library(ggsignif)     # CRAN v0.6.2
library(ggridges)     # CRAN v0.5.3
library(cowplot)      # CRAN v1.1.1

@@

## Weighted turnover over time course

```{r}
# Take peaks_mapped_summarized (which is the dataframe of IRMS values averaged across
# experimental and analytical replicates).
# Determine the weighted at2H, which is the sum of at2H values times relative area 
# divided by total area.

weighted_time_course <- peaks_mapped_summarized %>% 
  group_by(terrain, inc_time_d) %>%
  summarize(at2H_weighted = sum(at2H * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE))

peaks_mapped_summarized <- left_join(peaks_mapped_summarized, 
                                     weighted_time_course,
                                     by = c("terrain", "inc_time_d"))

@@

# Save Workspace Image
Handoff to paper plotting script

```{r}
# This will take a minute. 
# Uncomment below to save the workspace image.
# save.image(file = "cache/qSIP_calculations.RData")
```

# Practice Plotting

## Peak Tracer Incorporation
```{r}
peaks_mapped_with_zeros_analytes %>% ggplot(
  aes(x = inc_time_d, y = at2H, color = compound, group = compound)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "lm") +
  #geom_borderline() +
  scale_color_viridis_d() +
  theme_minimal()
```

@@

```{r}
peaks_mapped_summarized %>% 
  mutate(compound = forcats::fct_reorder(compound, rt)) %>% 
  ggplot(aes(x = inc_time_d,
             y = at2H,
             group = compound)) +
  geom_borderline(color = "gray") +
  geom_point() +
  geom_line(aes(x = inc_time_d,
                y = at2H_weighted,
                color = terrain),
            size = .8) +
  geom_point(aes(x = inc_time_d,
                y = at2H_weighted, 
                color = terrain),
             shape = 18,
             size = 3) +
  geom_label_repel(data = peaks_mapped_summarized %>% filter(inc_time_d == 7),
                   nudge_x = 2,
                   nudge_y = 0.005,
                   size = 2.5,
                   aes(label = compound)) +
  geom_label_repel(data = weighted_time_course %>% filter(inc_time_d == 3),
                   aes(x = inc_time_d,
                       y = at2H_weighted,
                       group = terrain,
                       color = terrain),
                   label = "Weighted Mean",
                   nudge_y = -.01,
                   nudge_x = 1,
                   size = 2.5) +
  facet_wrap(vars(terrain), nrow = 1) +
  scale_x_continuous(breaks = c(0, 3, 7)) +
  scale_color_npg() +
  coord_cartesian(xlim = c(0, 10), clip = FALSE) +
  labs(x = "Incubation Time (Days)",
       y = TeX("% $^2H$"),
       color = "Soil Type") +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank())
